Topics in Algorithms

### 2018-01-10 project/paper.tex
Added tree struct

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath,bm}            % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
\usepackage{parskip} 			   % no paragraph indentation
\usepackage{subcaption}

\usetikzlibrary{arrows,automata}

@@

@@

>>>>

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath,bm}            % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
\usepackage{parskip} 			   % no paragraph indentation
\usepackage{subcaption}
\usepackage{pgfplots}
\usetikzlibrary{arrows,automata}

@@

% argument #1: any options
\newenvironment{customlegend}[1][]{%
    \begingroup
    % inits/clears the lists (which might be populated from previous
    % axes):
    \csname pgfplots@init@cleared@structures\endcsname
    \pgfplotsset{#1}%
}{%
    % draws the legend:
    \csname pgfplots@createlegend\endcsname
    \endgroup
}%
\def\addlegendimage{\csname pgfplots@addlegendimage\endcsname}
\pgfkeys{/pgfplots/number in legend/.style={%
        /pgfplots/legend image code/.code={%
            \node at (0.125,-0.0225){#1}; % <= changed x value
        },%
    },
}
\pgfplotsset{
every legend to name picture/.style={west}
}

@@

\begin{figure}[H]
\begin{tikzpicture}[level distance=1.5cm,
  level 1/.style={sibling distance=3cm},
  level 2/.style={sibling distance=1.5cm}]
  \node[color=red] {$I'$}
    child[color=red] {node {$[0, ..., n/2]$}
    child[color=black,thick] {node[color=cyan] {$I^j$}}
      child[dashed] {node {$p(l_1)$}
      	child[solid, left=0.1cm, color=black] {node[color=cyan] {$l_1=[i_1, i_1+2]$}}
      	child[solid,color=black] {node[color=cyan] {$[i_1+2,i_1+4]$}}
      }
    }
    child[right=0.1cm, color=red] {node {$[n/2+2,...,n]$}
    child[color=black] {node[color=cyan] {$I^k$} 
    						child[dotted, color=black] {node {...}}
    						child[dotted, color=black,left=0.1cm] {node {...}}
    					}
      child[dashed] {{node {$p(l_2)$}
       	child[solid,color=black] {node[color=cyan] {$[i_2-4,i_2-2]$}}
      	child[right=1cm,solid,color=black] {node[color=cyan] {$l_2=[i_2-2, i_2]$}}
    }}};

\begin{customlegend}[legend cell align=left, %<= to align cells
legend entries={ % <= in the following there are the entries
$P$: path between $p(l_1)$ and $p(l_2)$,
 nodes belonging to $X$.
},
legend style={at={(0,2)},font=\footnotesize}] % <= to define position and font legend
% the following are the "images" and numbers in the legend
    \addlegendimage{solid,red}
    \addlegendimage{area legend,cyan, fill=cyan}
\end{customlegend}
\end{tikzpicture}
\caption{Lorem Ipsumthing}
\end{figure}
